

# (PART) Breakfast {-}

# Batters {#batter}


A lot of these are basically the same with some slight variations:
Flour, 
Water or milk, 
Salt, 
Sugar, 
Eggs.

Switch up the proportions slightly, cook it in something, and top with more sugar - be it powdered, liquified (i.e. syrup, amongst which Maple is king), or fruit - and call it a ~~day~~ morning.



## Dutch Baby


A Dutch baby is something weird, sort of a hybrid between a pancake and french toast, maybe. I like it, though I prefer waffles or french toast.


**Source:** I don't remember.


**Ingredients:**


```{r}



tbl <- data.frame(
  Ingredients = c( 
"1/2 cup flour",
"1/2 cup mulk", 
"3 eggs",
"1-2 tbsp sugar",
"4 tbls butter",
"1/2 - 1 tsp vanilla extract",
"1/2 tsp salt",
"1 tsp cinnamon"
),
  Tools = c("Cast iron skillet", "Mixing bowl", "Whisk", "Topping",
            "Powdered sugar", "Syrup (maple)", "Fried chicken", "Fruit")
)

idx <- which( str_detect(tbl[,2], "Topping" ) )

tbl %>%
  flextable() %>%
  theme_zebra() %>%
  align( part="all", align="left" ) %>%
  border_remove() %>% autofit() %>%
  bold( part="body", i=idx, j=2 ) %>%
  bg( part="header", i=1, j=1:2 , bg="grey85" ) %>%
  bg( part="body", i=idx, j=2 , bg="grey85" ) %>%
  border(  part="header", i=1, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=idx, j=2, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=nrow(tbl), j=1:2, border.bottom=h1  )





```



**Preparation:**

1. Preheat oven to 425.
2. Put butter in skillet and place in oven to melt.
3. Mix all of the other ingredients in a mixing bowl.
4. Once butter is melted and skillet it warm, remove from oven, pour in batter, and return to oven.
    - The skillet should be warm/hot, so that there is an immediate crisping of some of the batter. The whole thing will puff up a lot, but then collapse once you take it out.
5. Bake for 20 minutes. Then reduce temp to 300 and bake 5 more minutes.



**Variations:**

- Change the amount and/or type of spice to suit your taste. I like cinnamon, nutmeg works. Maybe thyme if you're weird.

**Notes:**

- This can be dairy-free by using dairy-free milk and butter.


















<!----------------------------------------------------------------------

                      NEXT RECIPE

----------------------------------------------------------------------->

## French Toast Batter


**Source:** [Serious Eats](https://www.seriouseats.com/2014/04/perfect-quick-and-easy-french-toast-recipe.html). They experimented, and I like their conclusions.


**Ingredients:**


```{r}



tbl <- data.frame(
  Ingredients = c( "2 eggs",
                   "2/3 cup milk (??? g)",
                   "1/2 tbsp sugar"
   ),
  Tools = c("Mixing bowl", "Whisk", "Frying pan")
)


tbl %>%
  flextable() %>%
  theme_zebra() %>%
  align( part="all", align="left" ) %>%
  border_remove() %>% autofit() %>%
  bg( part="header", i=1, j=1:2 , bg="grey85" ) %>%
  border(  part="header", i=1, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=nrow(tbl), j=1:2, border.bottom=h1  )





```



**Preparation:**

1. Set the pan to medium to start heating.
2. Whisk the eggs, then add the rest of the ingredients besides bread.
3. Sprinkle a little bit of sugar on the wet part of the batter when frying. It will carmalize and form a crisp little crust. But be CAREFUL, it will burn easily.


**Variations:**

- Add some cinnamon to the batter. I forget how much I use, will update next time I made french toast.

**Notes:**

- This can be dairy-free by using dairy-free milk.
- Recipie can be increased or decreased, egg-to-milk ratio should be approximately 1/3 cup of milk for each egg (or possibly slightly less, maybe 1/4 cup milk for each egg). the sugar-to-egg ratio should be about 1/4 tbsp sugar per egg.




<!----------------------------------------------------------------------

                      NEXT RECIPE

----------------------------------------------------------------------->

## Waffle Batter


Of the breakfast foods made with batter, waffles are the best. Crispy on the outside, soft on the inside, and you can pair it with fruit, syrup, or breaded chicken.

This recipe should make 4-8 waffles, depending on the size of your waffle iron.

**Source:** [Allrecipes](https://allrecipes.com/recipe/22180/waffles-i/amp/)


**Ingredients:**


```{r}

tbl <- data.frame(
  Ingredients = c( "2 cups flour (320 g)", 
                   "3 tbls sugar (40 g)",
                   "1/4 - 1 tsp salt (9 g)",
                   "4 tsp baking powder",
                   "2 eggs",
                   "1 3/4 cup milk (400 g)",
                   "1/2 cup oil",
                   "1/2 - 1 1/2 tsp vanilla extract"
   ),
  Tools = c("Mixing bowl x2", "Whisk", "Measuring cups", "Waffle iron",
            "Topping", "Butter & Syrup (maple, of course)", "Fried chicken",
            "Fruits and whipped cream")
)


idx <- which( str_detect(tbl[,2], "Topping" ) )

tbl %>%
  flextable() %>%
  theme_zebra() %>%
  align( part="all", align="left" ) %>%
  border_remove() %>% autofit() %>%
  bold( part="body", i=idx, j=2 ) %>%
  bg( part="header", i=1, j=1:2 , bg="grey85" ) %>%
  bg( part="body", i=idx, j=2 , bg="grey85" ) %>%
  border(  part="header", i=1, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=idx, j=2, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=nrow(tbl), j=1:2, border.bottom=h1  )





```


**Preparation:**

1. Set the waffle iron to start heating up.
2. Beat the eggs, then add the rest of the wet ingredients (milk, oil, vanilla) and mix.
3. Whisk the dry ingredients (flour, salt, sugar, baking powder) together. I usually do this seperately, but that probably doesn't matter.
4. Add the wet ingredients to the dry, and mix well.
5. TODO: Measure my waffle iron. Approx 3/4 cup of batter.


**Variations:**

- For Sourdough Waffles: Use 300 g starter. Reduce milk to 300 g and flour to 175 g.
- A different version of yeasted waffles, which doesn't require a sourdough started, is found at post number 5 by "Queen Bruin" [here](http://boards.straightdope.com/sdmb/showthread.php?t=426333). I tried it once and didn't find it worth the effort.

**Notes:**

- This can be dairy-free by using dairy-free milk.
- Don't always trust the time on the waffle iron. I just let it cook until it's basically done steaming, or a bit more.




<!----------------------------------------------------------------------

                      NEXT RECIPE

----------------------------------------------------------------------->



## Pancake Batter


Pankcakes are, well, they're okay.


**Source:** I don't remember.


**Ingredients:**


```{r}

tbl <- tibble(
  Ingredients = c( "1 1/2 cups flour (??? g)", 
                   "2 tbls sugar (??? g)",
                   "1/2 tsp salt (4-5 g)",
                   "1 1/2 - 2 tbsp baking powder",
                   "1 egg",
                   "1 1/4 cup milk (??? g)",
                   "3 tbsp oil",
                   "2 tsp vanilla extract"
   ),
  Tools = c("Mixing bowl", "Whisk", "Frying pan", "Spatula", rep( " ", 4) )
)


# idx <- which( str_detect(tbl[,2], "Topping" ) )

tbl %>%
  flextable() %>%
  theme_zebra() %>%
  align( part="all", align="left" ) %>%
  border_remove() %>% autofit() %>%
  #bold( part="body", i=idx, j=2 ) %>%
  bg( part="header", i=1, j=1:2 , bg="grey85" ) %>%
  #bg( part="body", i=idx, j=2 , bg="grey85" ) %>%
  border(  part="header", i=1, border.bottom=h1, border.top=h1 ) %>%
  #border(  part="body", i=idx, j=2, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=nrow(tbl), j=1:2, border.bottom=h1  )





```


**Preparation:**

1. Set the pan on medium heat to start warming.
2. Beat the eggs, add the rest of the wet ingredients (milk, oil, vanilla) and mix.
3. Whisk the dry ingredients (flour, salt, sugar, baking powder) together. I usually do this seperately, but that probably doesn't matter.
4. Add the wet ingredients to the dry, and mix, but leave a bit lumpy. Or mix until smooth. It doesn't matter that much.
5. Put however much you want into the pan at a time. Usually 1/2 - 3/4 cup is good.
6. Flip when the surface gets bubbly.

**Variations:**

- None that I've experimented with. I don't eat pancakes often.


**Notes:**

- This can be dairy-free by using dairy-free milk.



<!----------------------------------------------------------------------

                      NEXT RECIPE

----------------------------------------------------------------------->




