

# Other Breakfasts {#breakfast}



## Bacon sandwich

Yeah, a bacon sandwich is pretty basic. But I think there's enough variants


**Source:** Experimentation.


```{r}

tbl <- data.frame(
  Ingredients = c( "3-4 strips of bacon", 
                   "Bread or other bun",
                   "Mayonaise",
                   "Other dressings as desired"),
  Other = c("Bannana pepper mustard", "Fried egg", "Avocado/Guacamole", "Lettuce")
)


tbl %>%
  flextable() %>%
  theme_zebra() %>%
  align( part="all", align="left" ) %>%
  border_remove() %>% autofit() %>%
  bg( part="header", i=1, j=1:2 , bg="grey85" ) %>%
  border(  part="header", i=1, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=nrow(tbl), j=1:2, border.bottom=h1  )



```



**Preparation:**

1. Fry the bacon to your preference. I suggest using medium heat.
2. Toast the bread. You don't have to, but toasted > not, so why wouldn't you?



**Variations:**

- The recipe above is quite basic. The second column, "Other", are some extra toppings that I like. They go well individually or together.
- Bananna pepper mustard might be hard to find, but it's worth it. If I can find a link to the type I know and love, I'll put it here.


**Notes:**

- It's a sandwich, how difficult can it be?




<!----------------------------------------------------------------------

                      NEXT RECIPE

----------------------------------------------------------------------->



## Biscuits

Technically biscuits are more versatile than just using them for biscuits and gravy, but what's the point?



Initial comment

**Source:** [Allrecipes](https://allrecipes.com/recipe/22180/waffles-i/amp/)


**Ingredients:**


```{r}

tbl <- data.frame(
  Ingredients = c( "2 cups flour (320 g)", 
                   "3 tbls sugar (40 g)",
                   "1/4 - 1 tsp salt (9 g)",
                   "4 tsp baking powder",
                   "2 eggs",
                   "1 3/4 cup milk (400 g)",
                   "1/2 cup oil",
                   "1/2 - 1 1/2 tsp vanilla extract"
   ),
  Tools = c("Mixing bowl x2", "Whisk", "Measuring cups", "Waffle iron",
            "Topping", "Butter & Syrup (maple, of course)", "Fried chicken",
            "Fruits and whipped cream")
)


idx <- which( str_detect(tbl[,2], "Topping" ) )

tbl %>%
  flextable() %>%
  theme_zebra() %>%
  align( part="all", align="left" ) %>%
  border_remove() %>% autofit() %>%
  bold( part="body", i=idx, j=2 ) %>%
  bg( part="header", i=1, j=1:2 , bg="grey85" ) %>%
  bg( part="body", i=idx, j=2 , bg="grey85" ) %>%
  border(  part="header", i=1, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=idx, j=2, border.bottom=h1, border.top=h1 ) %>%
  border(  part="body", i=nrow(tbl), j=1:2, border.bottom=h1  )





```


**Preparation:**




**Variations:**



**Notes:**



















Biscuits

Gravey


Scramble

Huevos Rancheros



